Transfer of Value Functions via Variational Methods

### 2018-05-18 NIPS 2018/main.tex
Modified Related Works

In this section, we provide an experimental evaluation of our approach in four different domains with increasing level of difficulty. In all experiments, we compare our Gaussian variational transfer algorithm (GVT) and the version using a $c$-component mixture of Gaussians ($c$-MGVT) to plain no-transfer RL (NT) with $\epsilon$-greedy exploration. To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective. Thus, we provide a discussion of related works in the next section. \todo{Any better motivation?}

@@

Our approach is mostly related to \cite{lazaric2010bayesian}. Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian. On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators. Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves the importance of capturing more complicated task distributions again. In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over MDPs. unlike our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions. In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it. However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability. On the contrary, our approach can handle high-dimensional tasks. In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks. Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.

>>>>

In this section, we provide an experimental evaluation of our approach in four different domains with increasing level of difficulty. In all experiments, we compare our Gaussian variational transfer algorithm (GVT) and the version using a $c$-component mixture of Gaussians ($c$-MGVT) to plain no-transfer RL (NT) with $\epsilon$-greedy exploration. To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective. A comparative discussion of related works motivating this statement is provided in the next section.

@@

Our approach is mostly related to \cite{lazaric2010bayesian}. Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian. On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators. Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves the importance of capturing more complicated task distributions again. Finally, \cite{lazaric2010bayesian} considers the problem of jointly learning all given tasks, while we focus on transferring information from a set of source tasks to the target task. In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over MDPs. Unlike our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions. In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it. However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability. On the contrary, our approach can handle high-dimensional tasks. In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks. Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach. Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.
